### 2016-02-29 untitled.tex
Reviewer A and Reviewer B (first comment)

The advantage of the dynamic model is that it is more flexible since it does not impose any assumptions on control flow. The advantage of the segmented model is that is allows for more accurate analysis. The period enforcer algorithm and its analysis applies (only) to the segmented model.

@@

The central notation in Rajkumar's analysis~\cite{Raj:suspension1991} is a \emph{deferrable task}, which matches our notion of multi-segment tasks.  Specifically, Rajkumar states that:
\begin{quote}
With deferred execution, a task $\tau_i$ can execute its $C_i$ units of execution in discrete amounts $C_i^1, C_i^2$, $\ldots$ with suspension in between $C_i^j$ and $C_i^{j+1}$. \cite[Section 3]{Raj:suspension1991}\footnote{The notation has been altered here for the sake of consistency.} 
\end{quote}
%
Central to Rajkumar's analysis~\cite{Raj:suspension1991} is a \emph{task set transformation} that splits each deferrable task with multiple segments into a corresponding number of single-segment deferrable tasks.  In the words of Rajkumar~\cite[Section 3]{Raj:suspension1991}:

@@

One may consider to enrich the period enforcer with the following power: when the processor becomes idle, a task immediately becomes eligible to execute regardless of its eligibility time. However, even with this extension, the above example remains valid by introducing one additional lowest priority task $\tau_3$ with execution time $C_3=13$ (to be executed from time $3$ to time $9$ and time $13$ to time $20$) and $T_3=D_3=100$. With task $\tau_3$, the processor is always busy from time $0$ to time $23$ and consequently $\tau_2$ still misses its deadline at time $22$.

Furthermore, the example also demonstrates that the conversion to single-segment deferrable tasks does incur a loss of generality since it introduces pessimism: if we convert the two computation segments of task $\tau_2$ into two deferrable tasks $\tau_2^1$ and $\tau_2^2$, where  task $\tau_2^1$ never defers its execution and task $\tau_2^2$ defers its execution by at most \emph{$9$} time units,  then it is immediately obvious that the resulting single-segment deferrable task set $\{\tau_1, \tau_2^1, \tau_2^2\}$ is in fact not schedulable under a rate-monotonic priority assignment since we can time the release of a job of $\tau_1$ to coincide with the arrival of a job of $\tau_2^2$ after it has maximally deferred its execution, which clearly results in a deadline miss.

>>>>

A special case of the segmented self-suspending sporadic task model is the deferrable sporadic task model, in which each task $\tau_i$ starts with a self-suspension interval followed by one computation segment. The deferrable sporadic task model is the central notation in Rajkumar's analysis~\cite{Raj:suspension1991}. We will explicitly explain the link in Section~\ref{sec:classic-analysis}.

The advantage of the dynamic model is that it is more flexible since it does not impose any assumptions on the task control flow. The advantage of the segmented model is that it allows for more accurate analysis. The period enforcer algorithm and its analysis applies (only) to the segmented model.

@@

The central notation in Rajkumar's analysis~\cite{Raj:suspension1991} is a \emph{deferrable task}, which matches our notion of segmented tasks.  Specifically, Rajkumar states that:
\begin{quote}
With deferred execution, a task $\tau_i$ can execute its $C_i$ units of execution in discrete amounts $C_i^1, C_i^2$, $\ldots$ with suspension in between $C_i^j$ and $C_i^{j+1}$. \cite[Section 3]{Raj:suspension1991}\footnote{The notation has been altered here for the sake of consistency.} 
\end{quote}
%
Central to Rajkumar's analysis~\cite{Raj:suspension1991} is a \emph{task set transformation} that splits each deferrable task with multiple segments into a corresponding number of single-segment deferrable tasks.  In the words of Rajkumar~\cite[Section 3]{Raj:suspension1991}:

@@

One may consider to enrich the period enforcer with the following property: when the processor becomes idle, a task immediately becomes eligible to execute regardless of its eligibility time. However, even with this extension, the above example remains valid by introducing one additional lowest priority task $\tau_3$ with execution time $C_3=13$ (to be executed from time $3$ to time $9$ and time $13$ to time $20$) and $T_3=D_3=100$. With task $\tau_3$, the processor is always busy from time $0$ to time $23$ and consequently $\tau_2$ still misses its deadline at time $22$.

We can now examine why task $\tau_2$ misses the deadline by the period enforcer algorithm.

Clearly, the suspension time of task $\tau_2^1$ is $0$. The suspension time of task $\tau_2^2$ is $C_2^1+C_1+S_2^1=9$. In the worst case response time analysis, we can easily see that the worst-case response time of task $\tau_2^2$ is $2+1$ after the second computation segment arrives.

Furthermore, the example also demonstrates that the conversion to single-segment deferrable tasks does incur a loss of generality since it introduces pessimism. Recall that the analysis in Theorem 5 in~\cite{Raj:suspension1991} was only compatible with the deferrable task model. For the above example, we need to convert the segmented-suspending sporadic task $\tau_2$ into two deferrable tasks, called $\tau_2^1$ and $\tau_2^2$.
By converting the two computation segments of task $\tau_2$ into two deferrable tasks $\tau_2^1$ and $\tau_2^2$, we can conclude that  task $\tau_2^1$ never defers its execution and task $\tau_2^2$ defers its execution by at most \emph{$9$} time units.  Then the resulting single-segment deferrable task set $\{\tau_1, \tau_2^1, \tau_2^2\}$ is in fact not schedulable under the given fixed-priority scheduling since we can time the release of a job of $\tau_1$ to coincide with the arrival of a job of $\tau_2^2$ after it has maximally deferred its execution. We can easily see that the worst-case response time of the computation segment represented by task $\tau_2^2$ is $3$ time units after the second computation segment of task $\tau_2$ arrives. Together with the maximum deferred time $9$ time units, we know that the corresponding deferrable task set in fact has deadline misses since $9+3=12 > 11$. Therefore, the period enforcer algorithm may also cause a deadline miss.
